Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-30 PathModels.Rmd
re-render

```{r, load_function, include=FALSE}
# \\path (xd.north west) ++(-0.2, 3pt) node[above left]{(A)};
# \\path (xd.north west) ++(-0.4, 16pt) node[draw, above left, shape=circle, very thick, inner sep=2pt] {\\large \\textbf{<<fig_num>>}};
path_tikz_fig <- function(data) {
  glue::glue_data(data, 
"
\\begin{figure}
\\begin{center}
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};
\\end{tikzpicture}
\\end{center}
\\end{figure}
", 
.open = "<<", .close = ">>"
)
}

path_tikz <- function(data) {
  glue::glue_data(data, 
"
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};
\\end{tikzpicture}
", 
.open = "<<", .close = ">>"
)
}
```

>>>>

```{r, load_function, include=FALSE}
# \\path (xd.north west) ++(-0.2, 3pt) node[above left]{(A)};
# \\path (xd.north west) ++(-0.4, 16pt) node[draw, above left, shape=circle, very thick, inner sep=2pt] {\\large \\textbf{<<fig_num>>}};
path_tikz_fig <- function(data) {
  glue::glue_data(data, 
"
\\begin{figure}
\\begin{center}
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[latex-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[latex-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[latex-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};
\\end{tikzpicture}
\\end{center}
\\end{figure}
", 
.open = "<<", .close = ">>"
)
}

path_tikz <- function(data) {
  glue::glue_data(data, 
"
\\begin{tikzpicture}[font=\\sffamily]
    \\node[mynode] (m){<<lab_m>>};
    \\node[mynode,below left=of m](x) {<<lab_x>>};
    \\node[mynode,below right=of m](y) {<<lab_y>>};
    \\node[mynode,above left=of m](xd) {<<lab_x_direct>>};
    \\node[mynode,above right=of m](yd) {<<lab_y_direct>>};
    \\draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {<<coef_xy_direct>>} (yd.west);
    \\draw[latex-latex] (x.north) -- node[auto] {<<coef_xm>>} (m.west);
    \\draw[latex-latex] (m.east) -- node[auto] {<<coef_my>>} (y.north);
    \\draw[latex-latex] (x.east) -- node[below=2mm, align=center] {<<coef_xy>>} (y.west);
    \\path (xd.north west) ++(-0.2, 6pt) node[above left]{\\textbf{(<<fig_num>>) <<study_num>>}};
\\end{tikzpicture}
", 
.open = "<<", .close = ">>"
)
}
```

### 2023-05-30 PathModels.tex
re-render

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.40****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.41***} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.13} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1:}};
\end{tikzpicture}

@@

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.27****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.24****} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.07} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2:}};
\end{tikzpicture}

@@

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[-latex] (xd.east) -- node[above=2mm, align=center] {0.18****} (yd.west);
    \draw[-latex] (x.north) -- node[auto] {0.31****} (m.west);
    \draw[-latex] (m.east) -- node[auto] {0.23****} (y.north);
    \draw[-latex] (x.east) -- node[below=2mm, align=center] {0.10**} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3:}};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.30**} (yd.west);
    \draw[latex-latex] (x.north) -- node[auto] {0.39****} (m.west);
    \draw[latex-latex] (m.east) -- node[auto] {0.45***} (y.north);
    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.12} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(A) Study 1:}};
\end{tikzpicture}

@@

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.14***} (yd.west);
    \draw[latex-latex] (x.north) -- node[auto] {0.20****} (m.west);
    \draw[latex-latex] (m.east) -- node[auto] {0.22****} (y.north);
    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.09*} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(B) Study 2:}};
\end{tikzpicture}

@@

\begin{tikzpicture}[font=\sffamily]
    \node[mynode] (m){Interaction\\Quality};
    \node[mynode,below left=of m](x) {Core Need\\Fulfillment};
    \node[mynode,below right=of m](y) {Outgroup\\Attitudes};
    \node[mynode,above left=of m](xd) {Core Need\\Fulfillment};
    \node[mynode,above right=of m](yd) {Outgroup\\Attitudes};
    \draw[latex-latex] (xd.east) -- node[above=2mm, align=center] {0.18****} (yd.west);
    \draw[latex-latex] (x.north) -- node[auto] {0.31****} (m.west);
    \draw[latex-latex] (m.east) -- node[auto] {0.24****} (y.north);
    \draw[latex-latex] (x.east) -- node[below=2mm, align=center] {0.10***} (y.west);
    \path (xd.north west) ++(-0.2, 6pt) node[above left]{\textbf{(C) Study 3:}};
\end{tikzpicture}

### 2023-05-30 Robustness-Methods-and-Results.tex
re-render

To assess whether the need content (i.e., the motives) would impact the
effect of the need fulfillment experiences, we manually coded the topics
we extracted during the topic modeling on two dimensions of how much
they reflect a practical and a psychological goal-directedness. We chose
practical and psychological needs specifically as our dimensions to
account for differences in the types of needs that participants commonly
reported. With practical motives we refer to specific, tangible goals or
tasks that participants aimed to accomplish during the interaction.
These instrumental goals are usually observable, concrete, and often
centered on external outcomes, such as acquiring resources, completing
tasks, and addressing immediate challenges \citep[][]{}. With
psychological motives we refer to underlying motives or desires that are
more abstract and relate to personal fulfillment and well-being. In
contrast to practical needs, psychological needs delve into the
subjective and internal aspects of human experiences. These needs
pertain to emotions, social connections, and cognitive processes,
reflecting individuals' quest for personal growth, well-being, and
thriving in social relationships \citep[][]{}. Note that with this
approach any particular motive can include a practical and/or a
psychological goal-directedness but can also be classified as not having
any goal at all. The full coding protocol we developed with examples for
each of the codes is available in our Online Supplemental Material D.
After an initial training, each of the two coders independently coded
the 47 topics on the two dimensions, using one of three options each
(i.e., 0 = no goal, 1 = vague goal, 2 = clear goal). Inter-rater
reliability assessments showed that for both the practical as well as
the psychological needs, agreement was not optimal using the three
answer options (agreement practical = 0.72\%, agreement psychological =
0.78\%). However, most disagreements were, if a need was present,
whether that need was vague (1) or concrete (2). We, thus, collapsed
these two categories making the ratings binary (need absent vs.~need
present). With the simpler coding, inter-rater agreement for practical
needs (0.93\%) and the psychological need (0.96\%) were much more
reliable. Using Cohen's \(\kappa\) as our measure of inter-rater
reliability, we find that both the practical need coding
(\textit{Cohen's} \(\kappa\) = 0.80, 95\%CI{[}0.58, 1.00{]}) as well as
the psychological need coding (\textit{Cohen's} \(\kappa\) = 0.86,
95\%CI{[}0.67, 1.00{]}) were very good. We thus proceeded with this
collapsed coding. After resolving coder disagreements and merging the
codings back to the free-text responses, we found that a majority of
responses showed both a practical as well as a psychological need
(57.95\%) and only few responses had no goal at all (1.03\%) with the
remaining 41.02\% having either a practical or a psychological need only
(see Online Supplemental Material A for more detailed tables and
visualizations).

@@

Secondly, to assess whether the need fulfillment mechanism affected by
whether the interaction was accidental or planned we ran an exploratory
moderation analysis using the participants' ratings of how much they
perceived the interaction as `accidental'. It should be noted that we
asked our participants to focus on most the important interaction (i.e.,
``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'''\,'\,``;
emphasis as in original). We again start our analysis approach by
assessing the model across all three studies, using a three-level
hierarchical model. In this overall model, we retain the main effect of
core need fulfillment (random slopes model, grand-mean standardized to
account for all levels of variance; \textit{b} = 2.87, \textit{t}(
7.979) = 7.32, \textit{p} \textless{} .001, \textit{95\%CI}{[} 2.10,
3.64{]}) but neither contact intent nor the moderation effect affect the
results (all \textbar{}\textit{b}\textbar{} \textless{} 0.27 and all
\textit{p} \textgreater{} 0.225; see \tblref{tab:robustnessTblLong} for
full results).

@@

\paragraph{overall}

@@

\paragraph{Study follow-up}

>>>>

To assess whether the need content (i.e., the motives) would impact the
effect of the need fulfillment experiences, we manually coded the topics
we extracted during the topic modeling on two dimensions of how much
they reflect a practical and a psychological goal-directedness. We chose
practical and psychological needs specifically as our dimensions to
account for differences in the types of needs that participants commonly
reported. With practical motives we refer to specific, tangible goals or
tasks that participants aimed to accomplish during the interaction.
These instrumental goals are usually observable, concrete, and often
centered on external outcomes, such as acquiring resources, completing
tasks, and addressing immediate challenges \citep[e.g.,][]{oduntan2019}.
With psychological motives we refer to underlying motives or desires
that are more abstract and relate to personal fulfillment and
well-being. In contrast to practical needs, psychological needs delve
into the subjective and internal aspects of human experiences. These
needs pertain to emotions, social connections, and cognitive processes,
reflecting individuals' quest for personal growth, well-being, and
thriving in social relationships \citep[][]{dweck2017}. Note that with
this approach any particular motive can include a practical and/or a
psychological goal-directedness but can also be classified as not having
any goal at all. The full coding protocol we developed with examples for
each of the codes is available in our Online Supplemental Material D.
After an initial training, each of the two coders independently coded
the 47 topics on the two dimensions, using one of three options each
(i.e., 0 = no goal, 1 = vague goal, 2 = clear goal). Inter-rater
reliability assessments showed that for both the practical as well as
the psychological needs, agreement was not optimal using the three
answer options (agreement practical = 0.72\%, agreement psychological =
0.78\%). However, most disagreements were, if a need was present,
whether that need was vague (1) or concrete (2). We, thus, collapsed
these two categories making the ratings binary (need absent vs.~need
present). With the simpler coding, inter-rater agreement for practical
needs (0.93\%) and the psychological need (0.96\%) were much more
reliable. Using Cohen's \(\kappa\) as our measure of inter-rater
reliability, we find that both the practical need coding
(\textit{Cohen's} \(\kappa\) = 0.80, 95\%CI{[}0.58, 1.00{]}) as well as
the psychological need coding (\textit{Cohen's} \(\kappa\) = 0.86,
95\%CI{[}0.67, 1.00{]}) were very good. We thus proceeded with this
collapsed coding. After resolving coder disagreements and merging the
codings back to the free-text responses, we found that a majority of
responses showed both a practical as well as a psychological need
(57.95\%) and only few responses had no goal at all (1.03\%) with the
remaining 41.02\% having either a practical or a psychological need only
(see Online Supplemental Material A for more detailed tables and
visualizations).

@@

Secondly, to assess whether the need fulfillment mechanism affected by
whether the interaction was accidental or planned we ran an exploratory
moderation analysis using the participants' ratings of how much they
perceived the interaction as `accidental'. It should be noted that we
asked our participants to focus on most the important interaction (i.e.,
``\textit{The following questions will be about the interaction \underline{you consider most significant}.}'';
emphasis as in original). We again start our analysis approach by
assessing the model across all three studies, using a three-level
hierarchical model. In this overall model, we retain the main effect of
core need fulfillment (random slopes model, grand-mean standardized to
account for all levels of variance; \textit{b} = 2.87, \textit{t}(
7.979) = 7.32, \textit{p} \textless{} .001, \textit{95\%CI}{[} 2.10,
3.64{]}) but neither contact intent nor the moderation effect affect the
results (all \textbar{}\textit{b}\textbar{} \textless{} 0.27 and all
\textit{p} \textgreater{} 0.225; see \tblref{tab:robustnessTblLong} for
full results).

@@

@@

### 2023-05-30 Table.tex
Table General Footnote
re-render

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont (Intercept)} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 68.15**** [65.25, 71.06]} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.29* [ 0.02,  0.56]; $\eta_{partial}$ = 0.08} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.23 [-5.03,  9.48]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -3.15 [-7.78,  1.48]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:AvQualityOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.02,  0.01]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46 [-1.17,  0.24]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.46* [-0.92, -0.01]; $\eta_{partial}$ = 0.02} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.46 [-0.30,  1.23]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityOut:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.16 [-0.24,  0.56]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont $R^2 / R^2_{adjusted}$} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.139 / 0.098} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}->{\huxb{0, 0, 0}{0.4}}-}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}

>>>>

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont (Intercept)} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 68.24**** [65.30, 71.18]} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.27* [ 0.03,  0.50]; $\eta_{partial}$ = 0.05} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  2.50 [-4.86,  9.85]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -2.97 [-7.67,  1.72]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:AvQualityCombOut} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.03,  0.00]; $\eta_{partial}$ = 0.01} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.38 [-1.14,  0.37]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.45 [-0.91,  0.02]; $\eta_{partial}$ = 0.02} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut:studyNum1} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.07 [-0.76,  0.90]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont AvQualityCombOut:studyNum3} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont -0.01 [-0.35,  0.33]; $\eta_{partial}$ = 0.00} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

@@

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont $R^2 / R^2_{adjusted}$} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont 0.118 / 0.076} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{>{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}->{\huxb{0, 0, 0}{0.8}}-}
\arrayrulecolor{black}

\multicolumn{9}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont Note:$<$br$>$**** p $<$ .0001, *** p $<$ .001, ** p $<$ .01, * p $<$ .05} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

\hhline{}
\arrayrulecolor{black}
\end{tabular}
\end{threeparttable}\par\end{centerbox}
